### 2017-03-24 paper/evaluation.tex
updated plots
pass on subjs

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQD}{RQ4}
\newcommand{\numRQE}{RQ5}
\newcommand{\numRQF}{RQ6}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  regression test suites in open-source projects?}
\newcommand{\RQB}{How time is distributed across test cases?}
\newcommand{\RQC}{How often parallelization settings appear in build
  files?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQE}{What factors contribute to improve performance
  through parallelization?\Jbc{Previously as "When does
    parallelization works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of parallelization?}

\begin{itemize}
    \item \textbf{\numRQA.} \RQA
    \item \textbf{\numRQB.} \RQB
    \item \textbf{\numRQC.} \RQC
    \item \textbf{\numRQD.} \RQD
    \item \textbf{\numRQE.} \RQE
    \item \textbf{\numRQF.} \RQF
\end{itemize}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects. The second research question addresses
the balance of regression tests: we want to investigate how the time
cost is distributed among test cases. The third
research question addresses our interest in understanding if
developers are aware of parallelization features from testing
frameworks available out-of-the-box through build systems (\eg, run
JUnit test cases in parallel using Maven Surefire) and what settings
are more often used.  The fourth research question addresses the
impact of parallelism on the regression tests from our sample set. For
subjects that use parallelization settings, we are interested in
compare the execution performance when these settings are activated
and deactivated (\ie, sequential execution) to evaluate the benefits.
\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
addresses the characteristics of regression tests from the previous
experiment.  More specifically, we want to investigate if there is a
relation between the balance of test execution (\ie, how uniformly
distributed is the execution time across tests cases) and the usage of
computational resources (\ie, if tests are mostly CPU or IO intense)
that impacts the effectiveness of parallelization}.  Finally, the
sixth research question discusses the limitations and insights to
overcome the pitfalls of parallelization.

@@

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from \github{}.  We are
interested to evaluate non-trivial test suites on popular projects
that are in activity. We used the \github{}'s search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the \github{} API considers
the predominant language as the primary language.}; (2) the project
has at least 100 stars; (3) latest update on (or after) January 1st,
2016; (4) the \emph{readme} file contains the string \emph{mvn}.

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
        +stars:>=100+pushed:>=2016-01-01
        +mvn%20in:readme+sort:stars
\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

A Maven project may contain several sub-modules with multiple \pomf{}
files. We considered only projects with a \pomf{} file located in the
root directory.  As of December 30th 2016, our search criteria
returned 615 subjects. From the 615 downloaded projects, 46 were not
Maven projects (or did not have a \pomf{} in the root directory) and
159 were in a unstable revision.  From these 159 unstable subjects,
\Jbc{elaborate what is unstable (\eg, (1) how many could not resolve
dependencies? (2) how many could not compile sources and tests? (3)
could not run tests due to incompatible testing environment?}. Our
final set consists in \numSubjs{} testable subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests. \Jbc{Be clear about
checking the elapsed time }.  Figure~\ref{fig:mvn-execution} shows the
commands used in our script to test each subject. The main loop (lines
5-11) iterates over the list of subjects and invokes Maven in
separated steps (lines 7-9). To avoid inflating the measured time we
executed Maven in different steps: we first compiled the source and
test files (line 7), made all dependencies available locally (line 8)
and later, we ran the tests in offline mode (line 9) to bypass package
updates. After the execution, we used a regular expression on the
output log to extract the elapsed time (line 10). Before collecting
the time cost, we executed all subjects and randomly selected 100 logs
to inspect and identify non-related tasks (\eg, \emph{javadoc}
generation and static analysis) to ignore during the experiment (lines
1-3).  To avoid noise from operating system events, we used a
dedicated server remotely via SSH with the operating system running
only essential services (\eg, the SSH server). In addition, we
configured the \CodeIn{isolcpus} option from the Linux Kernel
\cite{linux-kernel} to isolate six virtual CPUs to execute our
experiment and the remaining CPUs to run the operating system. By
isolating a set of virtual CPUs, we prevent context-switching from
experiment processes and OS-related processes.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.21\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/barplot-timecost.pdf}
        \caption{\label{fig:rq1-barplot}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/boxplot-timecost.pdf}
        \caption{\label{fig:rq1-boxplot}}
    \end{subfigure}%
    \caption{(a) Subjects grouped by time cost ($t$): short run ($t <
    1m$), medium run ($1m \le t < 5m$), and long run ($5m \le t$); (b)
    Distribution of time cost by group.}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallel modes
    identified in a subset of \numProjectsPar{} projects (unused modes
    omitted). A single project may have support to more than one
    parallel mode.}
\end{figure}

>>>>

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQD}{RQ4}
%%\newcommand{\numRQE}{RQ5}
\newcommand{\numRQF}{RQ5}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost is distributed across test cases?}
\newcommand{\RQC}{How often parallelization settings appear in build
  files?}
\newcommand{\RQD}{What is the impact of parallelization?}
%%\newcommand{\RQE}{What factors contribute to improve performance
%%  through parallelization?\Jbc{Previously as "When does
%%    parallelization works and when it does not so great?"}}
\newcommand{\RQF}{What are the limitations of low-level parallelism?}

\begin{itemize}
    \item \textbf{\numRQA.} \RQA
    \item \textbf{\numRQB.} \RQB
    \item \textbf{\numRQC.} \RQC
    \item \textbf{\numRQD.} \RQD
%%    \item \textbf{\numRQE.} \RQE
    \item \textbf{\numRQF.} \RQF
\end{itemize}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses the relationship of test cases and the overall execution
cost: we are interested to investigate how the time cost is
distributed among test cases.  In the third research question, we are
in understanding if developers are aware of low-level parallelism
features available out-of-the-box through build systems (\eg,
configuring Maven to use JUnit with multiple threads to speedup test
execution). In addition, we want to identify which configurations are
often used and why they more popular (if any).  The fourth research
question addresses the impact of low-level parallelism on the
regression tests from our sample set. For subjects that use
parallelization settings, we are interested to compare the execution
performance when these settings are activated and deactivated (\ie,
tests run sequentially).
%%\Jbc{This RQ has to be reworked:} \Fix{The fifth research question
%%addresses the characteristics of regression tests from the previous
%%experiment.  More specifically, we want to investigate if there is a
%%relation between the balance of test execution (\ie, how uniformly
%%distributed is the execution time across tests cases) and the usage of
%%computational resources (\ie, if tests are mostly CPU or IO intense)
%%that impacts the effectiveness of parallelization}.
Finally, the fifth research question discusses the limitations and
insights to overcome the pitfalls of parallelization.

@@

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from \github{}.  We are
interested to evaluate non-trivial test suites on popular projects
that are in activity. We used the \github{}'s search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the \github{} API considers
the predominant language as the primary language.}; (2) the project
has at least 100 stars; (3) latest update on (or after) March 1st,
2017; (4) the \emph{readme} file contains the string \emph{mvn}.

@@

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
        +stars:>=100+pushed:>=2017-03-01
        +mvn%20in:readme+sort:stars
\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on March 1st, 2017 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

A Maven project may contain several sub-modules with multiple \pomf{}
files. We considered only projects with a \pomf{} file located in the
root directory.  As of March 24th 2017, our search criteria returned
\Fix{615} subjects. From the \Fix{615} downloaded projects, \Fix{46}
were not Maven projects (or did not have a \pomf{} in the root
directory) and 159 were in a unstable revision.  From these 159
unstable subjects, \Jbc{elaborate what is unstable (\eg, (1) how many
could not resolve dependencies? (2) how many could not compile sources
and tests? (3) could not run tests due to incompatible testing
environment?}. Our final set consists in \numSubjs{} testable
subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  Also, measured the
approximated overhead from the build system after skipping non-related
tasks. We identified the generated test reports and compared the
difference between the elapsed time reported from Maven and the sum of
all test cases executed.
To avoid noise from operating system events, we used a dedicated
server remotely via SSH with the operating system running only
essential services (\eg, the SSH server). In addition, we configured
the \CodeIn{isolcpus} option from the Linux Kernel \cite{linux-kernel}
to isolate six virtual CPUs to execute our experiment and the
remaining CPUs to run the operating system. By isolating a set of
virtual CPUs, we prevent context-switching from experiment processes
and OS-related processes.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/barplot-timecost.pdf}
        \caption{\label{fig:rq1-barplot}}
    \end{subfigure}%
    \qquad
    \begin{subfigure}{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plots/boxplot-timecost.pdf}
        \caption{\label{fig:rq1-boxplot}}
    \end{subfigure}%
    \caption{(a) Subjects grouped by time cost ($t$): short run ($t <
    1m$), medium run ($1m \le t < 5m$), and long run ($5m \le t$); (b)
    Distribution of time cost by group.}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/parallel-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallel modes
    identified in a subset of \numProjectsPar{} projects (unused modes
    omitted). A single project may have support to more than one
    parallel mode.}
\end{figure}
